Simulations to test ctwas summary stats version, 45k samples, a few new setings required

### 2023-05-08 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45_03222023.Rmd
110k simulation

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)
```

>>>>

simutags <- paste(6, 1:20, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(7, 1:20, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(8, 1:20, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(9, 1:20, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)
```
